---
title: "Intro To Stats 4-10 Commit1"
author: "Richard"
date: "December 10, 2015"
output: html_document
---
This is the R Markdown for Problem 4-10 in Intro to Statistical Learning book.

1. Load the data
```{r}
library(data.table)
library(ISLR)
data("Weekly")
names(Weekly)
attach(Weekly)
```

2.1 Summarize the data
```{r}
summary(Weekly)
```

2.2 Correlation between each predictor and output
```{r}
pairs(Weekly)
cor(Weekly[,-ncol(Weekly)])
```
Conclusion1 Obvious correlation between volume and year

3.1 Test the significance of each predictor
```{r}
glm.fit=glm(Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, data=Weekly ,family=binomial)
summary(glm.fit)
```

3.2 Compute the coefficients of the model
```{r}
coef(glm.fit)
summary(glm.fit)$coef
```

3.3 Convert probabilities to indicators, Up and Down
```{r}
glm.probs=predict(glm.fit,type="response") 
contrasts(Weekly$Direction)
```

3.4 Calculate confusion matrix and the probability of making right prediction
```{r}
glm.pred=rep("Down","Up",nrow(Weekly))
glm.pred[glm.probs >.5]="Up"
table(glm.pred,Direction)
mean(glm.pred==Direction)
```

4.1 Split data into training and testing datasets
```{r}
train =( Year <= 2008)
Weekly.testing= Weekly [! train ,]
```

4.2 Fit and summarize a Logistic Model based on Lag2 only
```{r}
glm.fit=glm(Direction~Lag2,data=Weekly ,family=binomial, subset=train)
summary(glm.fit)
```

4.3 Calculate confusion matrix and the probability of making right prediction
```{r}
glm.probs=predict(glm.fit,Weekly.testing,type="response")
glm.pred=rep("Down",nrow(Weekly.testing))
glm.pred[glm.probs >.5]="Up"
table(glm.pred,Weekly.testing$Direction)
mean(glm.pred==Weekly.testing$Direction)
#Logistic Model, Using Lag2 as the only predictor,Prob=0.625
```

5.1 Fit the Model using Linear Discriminant Analysis
```{r}
library(MASS)
lda.fit = lda(Direction ~ Lag2, data=Weekly, subset=train)
lda.fit
```

5.2 Calculate confusion matrix and the probability of making right prediction
```{r}
lda.class=predict(lda.fit,Weekly.testing)$class
table(lda.class,Weekly.testing$Direction)
mean(lda.class==Weekly.testing$Direction)

```

6.1 Fit the Model using Quadratic Discriminant Analysis
```{r}
qda.fit = qda(Direction ~ Lag2, data=Weekly.testing, subset=train)
qda.fit
```

6.2 Calculate confusion matrix and the probability of making right prediction
```{r}
qda.class=predict(qda.fit,Weekly.testing)$class
table(qda.class,Weekly.testing$Direction)
mean(qda.class==Weekly.testing$Direction)
```

7.1 Fit the Model using KNN 
```{r}
library(class)
train.X=Weekly[train,"Lag2",drop=F]
test.X=Weekly[!train,"Lag2",drop=F]
train.Direction=Weekly[train,"Direction",drop=T]
test.Direction=Weekly[!train,"Direction",drop=T]
```

7.2 Using k=5, calculate confusion matrix and the probability of making right prediction
```{r}
set.seed(1)
knn.pred=knn(train.X,test.X,train.Direction,k=5)
table(knn.pred,test.Direction)
mean(knn.pred==test.Direction)
```